Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-08 article.rnw
Add a post processing function for printing coclassification matrices as heat maps.
Remove pgfplotstable-color-cells.tex.
The R code renders it irrelevant.
Fix an incorrect species in the phylogenetic tree.
Add the coclassification matrices to the article.

@@

\import{latex/}{forest-phylogeny}
\import{latex/}{pgfplotstable-color-cells}

@@

\begin{figure}
	\centering
	\begin{forest} phylogeny
		[
			[
				[
					[\emph{D. melanogaster}]
					[\emph{D. birchii}]
				]
				[
					[\emph{D. pandora}]
					[\emph{D. pseudoananassae}]
				]
			]
			[
				[
					[\emph{D. pallidifrons}]
					[\emph{D. sulfurigaster}]
				]
			]
		]
	\end{forest}

@@

>>>>

\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}

@@

\import{latex/}{forest-phylogeny}

@@

\begin{figure}
	\centering
	\begin{forest} phylogeny
		[
			[
				[
					[\emph{D. simulans}]
					[\emph{D. birchii}]
				]
				[
					[\emph{D. pandora}]
					[\emph{D. pseudoananassae}]
				]
			]
			[
				[
					[\emph{D. pallidifrons}]
					[\emph{D. sulfurigaster}]
				]
			]
		]
	\end{forest}

@@

\section{Results}

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_col_coclassification_matrix,
				colourmap="coclassification"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}

	\bigskip

	\begin{subfigure}{\textwidth}
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_row_coclassification_matrix,
				colourmap="coclassification"
			)
		@
		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
		\label{fig:coclassification-rows}
	\end{subfigure}

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by AIC weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
		\Cref{fig:coclassification-cols} represents the grouping of species' competetive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}
